Incentivizing Exploration with Unbiased History

### 2018-10-28 3level.tex
added intuition in 3level

They main idea for the 3-level policy is that it inserts the second level as an additional ``checkpoint'' to induce more adaptivity in the exploration. While the first level ensures that the agents explore both arms, the second level will continue to explore both arms only if the rewards of the two arms are still indistinguishable (that is, when $|\mu_1 - \mu_2| < \tilde{O}(1/\sqrt{T_1})$). In the third level, agents will pull the best arm unless $|\mu_1-\mu_2|$ is much smaller than $\tilde{O}(1/\sqrt{T_2})$, in which case pulling either arm will
incur small regret. \nicomment{Need to add intuition about why it's necessary to have a middle level to get this to happen, as opposed to making the bottom level bigger.  Is it because the bottom level will start to herd on some arm and we want to refresh that process? Also should talk about need for anti-concentration bound.} The formal guarantee of the policy is the
following.

>>>>

They main idea for the 3-level policy is that it inserts the second level as an additional ``checkpoint'' to induce more adaptivity in the exploration. \niedit{While the first level ensures that the agents explore both arms, the better arm can only be discovered if the gap in their rewards $|\mu_1-\mu_2|$ is sufficiently high.  When this gap is small (that is, when $|\mu_1 - \mu_2| < \tilde{O}(1/\sqrt{T_1})$), we argue that the second level will continue to explore both arms.  Here we use the anti-concentration bound to show each arm is ``lucky'' in at least one first level group (that is, for some first level group, its empirical mean is significantly larger than its mean whereas the other arm's empirical mean is significantly smaller than its mean).  Therefore, the corresponding second level group will explore the lucky arm, giving the third level refined estimates of each arm's mean.}  In the third level, agents will pull the best arm unless $|\mu_1-\mu_2|$ is much smaller than $\tilde{O}(1/\sqrt{T_2})$, in which case pulling either arm will
incur small regret. The formal guarantee of the policy is the
following. \nicomment{I'm a little confused why this works while simply growing the first level doesn't work; wouldn't the first level where the arm is ``lucky'' explore it more if it had more time?}
